Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-10-09 paper.tex
final modifications

            \tristan{It could be useful to refer to this special issue on workflows
            in neuroimaging in intro:
            https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2844796/}
            \tristan{This special issue on data sharing is also worth citing:
            https://www.sciencedirect.com/journal/neuroimage/vol/124/part/PB}
            In contrast, large datasets consist of many images acquired from
            multiple subjects, which are too large to be processed in their
            entirety. Notable examples of these datasets include the 
            Alzheimer's Disease Neuroimaging Initiative 
            (ADNI)~\cite{doi:10.1002/jmri.21049}, 
            OpenfMRI~\cite{POLDRACK2017259}, 
            the Autism Brain Imaging Data Exchange 
            (ABIDE)~\cite{Di-Martino:2013aa}, the Consortium for
            Reliability and Reproducibility (CoRR)~\cite{Zuo:2014aa}, the Human 
            Connectome Project (HCP)~\cite{VANESSEN201362} and the UK 
            Biobank~\cite{Miller:2016aa}, with the later
            two being flagship recent examples of large datasets in 
            neuroimaging.

@@

            OpenfMRI is a public repository originally conceived for the sharing
            of task-based fMRI data. Over time, it has grown to include EEG, MEG,
            resting-state fMRI (R-fMRI) and diffusion fMRI. Data made 
            available through
            OpenfMRI are obtained from both healthy and clinical individuals.
            Raw data must be made available for all datasets published to 
            OpenfMRI, however, preprocessed data may also accompany the raw data
            . At present, OpenfMRI houses data of a total 3372 subjects
            originating from 95 studies \note{obtained from website}.

@@

            The Consortium for Reliability and Reproducibility 
            \tristan{expand acronym} was developed as an initiative to study 
            and improve the 
            reliability and reproducibility of functional connectomics. The 
            data made available by the Consortium consists of test-retest data 
            obtained from 33 datasets. The repository contains data from 1629 
            subjects, in which anatomical, R-fMRI, dMRI, CBF and ASL scans are 
            available \note{obtained from website}.

@@

            All these initiative stress the importance of data-sharing and
            large-scale studies for the advancement of science. Many researchers
            are limited to the processing of subsets of the data available as 
            they lack compute and storage resources to process the data in its
            entirety. It is also important to note that many of the pipelines 
            developed by these initiatives made use of popular neuroimaging 
            toolboxes, such as FSL~\cite{SMITH2004S208} \tristan{You should cite it the first time you mention it}, FreeSurfer, ANTS, 
            CIVET, rather than
            creating their own. Therefore, there is a great need for Big Data
            frameworks that can leverage existing tools for the efficient 
            processing of large-scale datasets. Widespread availability and 
            accessibility of such frameworks will in turn lead to a greater
            volume of higher-impact studies.

@@

        For a workflow engine to be considered successful, it must be simple to 
        compose workflows using that framework. New researchers should be able 
        to acquire the skills to compose worfklows without
        investing a significant amount of time in understanding it. Reuse of
        existing tools is also common occurrence in neuroinformatics, and 
        workflow engines need to accomodate this by undertaking a modular 
        approach and being easily extensible. With the sharing of data also 
        comes the sharing of workflows. For labs to share their workflows with
        the community at large, these workflows must be easily understood by the
        community. This relates to the reproducibility of studies, as it is 
        more than likely that easily understood workflows are reproducible. 
        \tristan{Perhaps mention that this also relates to the sharing
        of reproducible results -- VH: not sure if this is what you meant --
        yeah, we might want to explicit this further in the paper but
        good enough for now}.

@@

            Many researchers have been exposed to Shell scripting languages as 
            several scientific workflows are composed in UNIX-based 
            environments. These environments typically have Make installed by
            default eliminating the need for users to install it manually.
            These features make workflow engine Make desirable for scientific
            computing.
            As Make is exclusive to UNIX environments, it is not 
            platform-independent. However, Make has the flexibility of being
            easily extensible and can interface directly with any command-line
            tool. Shell scripting, nevertheless, is generally not as intuitive
            as programming languages like Python and MATLAB.

@@

            Another example of a DSL is the Common Workflow
            Language (CWL). CWL can be seen in workflow engines like Toil. 
            It is similar to XML in that its main difference is that it is 
            YAML/JSON-based. \tristan{Review the previous sentence, it doesn't make sense. And the end of the paragraph is till fuzzy too}
            \tristan{It is a YAML-based DSL for workflows. Just like Pegasus' DAX is an XML-based DSL}. Files can either be written in JSON or YAML formats. CWL is 
            based on workflow engines like Make \tristan{? I don't think CWL relies on make, does it?}, but differs in that tasks
            are isolated \tristan{inputs and outputs are somewhat explicit in a Makefile}. Similarly to 
            make, CWL is only available on Linux and OSX platforms \tristan{strange, the CWL interpreter is in Python so I'd expect it to run anywhere}. \note{cite cwl 
            website}

            Programming language-based DSL workflow engines include OpenMOLE, which is  
            derived from Scala, and Nextflow, which is derived from the Apache 
            Groovy programming language. While both are written on top of the 
            Java platform, Nextflow is only compatible with Linux and OSX \tristan{How about using Linux everywhere instead of UNIX-based? You still have UNIX here and there.} 
            environments. These programming languages are not otherwise commonly
            used in neuroimaging, meaning that users must learn specific 
            languages that would not otherwise be used in their field.

@@

                The data structures made available by workflow engines dictate
                the maximum performance available to a workflow. \tristan{I don't understand the previous sentence, 
                in particular the 'maximum' idea. You should review that.} Scientific
                workflows are generally file-based, meaning that data, in the 
                form of files, will be 
                transferred across the network and I/O must be
                performed at each workflow activity. It is possible for some 
                data to remain in memory with scientific workflows, but these 
                are typically basic types such as numbers, strings and lists.
                More complex types, however, can be seen in workflow engines 
                such as PSOM which accept nested structures as long as the
                structures's terminal fields are either strings or cells of 
                strings. Due to workflow engines being file-based, performance
                is limited, particularly with Big Data.

@@

                Dask builds off of Spark by not only providing data 
                structures similar to Spark's RDDs and Dataframes, Dask Bag and 
                DataFrame, but by also providing an abstraction for 
                larger-than-memory matrices, the Dask array. Furthermore, it is
                possible to use common Python APIs (e.g. NumPy\note{cite} and 
                Pandas DataFrame~\cite{mckinney2011pandas}) to process the 
                data \tristan{I think Dask provides clones of these libraries, but you can't use
            them directly}. Although Spark does not have a datastructure for large 
                matrices, it has an RDD-based API, known as \textit{linealg}
                for similar processing of large 
                matrices~\cite{BosaghZadeh:2016:MCO:2939672.2939675}.

@@

            Nipype's wrapper, written in Python, can encapsulate CLIs, SPM, 
            MATLAB and Python scripts. InputSpec and OutputSpec are two classes 
            that can are used to describe the inputs and outputs of the 
            interface. The former defines the input parameters of 
            a command and the latter defines the outputs that are possibly 
            generated by the command. For CLIs, it is necessary to describe the
            command, such as order of parameters and required and optional parameters. 
            Apart from Input and Output Spec, a Python dictionary containing all
            expected outputs can be included.
            Before executing a CLI, Nipype can start X virtual framebuffer if 
            user interaction through a GUI is required by the tool if specified. 
            For SPM interfaces, the job 
            type and name must be specified. Interfaces to MATLAB require 
            definition of the run function, while Python interfaces require
            the definition of the \textit{\_run\_interface} function. \note{from
            website}.
            \tristan{Expand UDF, CLI, CARE.}

@@

            OpenMOLE has the ability to encapsulate UDF Scala scripts and CLI. 
            In the case of CLI tasks, it is also possible to containerize or 
            encapsulate with CARE \note{cite} to make it portable. OpenMOLE
            defines several classes to allow for the execution of different 
            types of tools. Like other framworks, it is vital to describe the
            inputs and outputs of the Tasks such that the execution of tasks 
            can be performed.

@@

            LONI enables generation of 
            the XML-based module interface through its GUI. The module interface
            consists of details on \note{from website} module metadata (e.g.
            authors, package, version, name) and citation information, 
            command-line syntax, parameter and file types, dependencies and 
            output and error handling.

@@

            Tool addition in Taverna is primarily performed through the user 
            interface, but can also achieved through the creation of an XML
            descriptor. Taverna differs from other workflow engines in that it
            can 
            execute generic-style services (i.e. WSDL and REST) in addition to
            other types of Web Services, external CLIs, R scripts and
            Java services. To interface with a CLI, the XML file must contain 
            the command to execute, file inputs and outputs (if required), if 
            standard input, output and error streams must be conserved and the 
            location where the command should execute\note{from website}.

            Pegasus is another workflow engine that uses an XML format to 
            define the CLI tools interface. The XML interfaces are typically 
            incorporated directly into the workflow DAX definition. However, a 
            separate multiline text-based 'Transformation Catalogue' file can
            be provided. Information encoded within the interfaces include
            tool identifier (typically namespace::version), the URL or filepath
            to the executable, site identifier of the executable's host, 
            executable type (e.g. installed or staged) and the profile. In
            addition to UDFs and CLIs, Pegasus
            can also execute containerized tools. For this, a container 
            identifier, image URL, site identifier of the image, and container
            profiles must also be defined \note{from website}.

@@

            Big Data frameworks such as MapReduce, Spark and Dask do not have   
            any form of checkpointing functionality outside of a given          
            execution. For instance, it is possible to checkpoint an RDD, but   
            that RDD will only be accessible within the application's context   
            and will not be shared with future executions. As failures do       
            happen and individual neuroimaging tasks may take a non-negligable  
            amount of time to execute, a mechanism to checkpoint workflows      
            will need to be added to any Big Data framework used for             
            neuroinformatics.                                                   
            \note{dont know how Taverna, Pegasus, Galaxy or Toil achieves this} 
            \note{openMole says it checks to see if outputs exist. similar to   
            make?}                                                              
            \note{what about SPM, FastR??}

@@

            \subsection{NIDM-Results}
                NIDM-results was designed to improve the limited XML-based 
                Clinical and Experimental Data Exchange (XCEDE) neuroimaging
                provenance metadata format~\cite{Maumet:2016aa}. It is a domain-specific extension
                to the W3C PROV model that aims to provide comprehensive and
                machine-readable provenance from raw data to its final stage. \tristan{give example? -- vhs: like a figure? No, like what can be described which couldn't in BIDS. 
                Forget about it for the comp exam, keep this note for the paper.}
                However, it is currently limited in the provenance 
                information it can provide, such as details on computational 
                environments. It is also limited by the fact that consensus lacks
                within the community on paradigms. \tristan{I disagree with the last sentence
                but this is fine. The main limitation imo is due to the use of RDF and an ontology: it is
                very powerful but difficult to use: performance sucks, queries are hell to write, 
                and format is not human-readable.}

@@

            \tristan{The rest of this section is very difficult to read because
            it lacks structure. Perhaps you could classify provenance tracking in PROV-based, lineage-based,
            and other custom formats? -- It is still a bit 'boring' :) No worries for the comp report,
            but could be discussed and fixed in the paper.}
            At minumum, provenance tracking should include 
            capturing details on the workflow stages as well as the inputs and
            outputs. LONI, Pegasus, Pydpiper and Galaxy all satisfy this 
            requirement, but store the data differently. LONI stores this 
            information in an XML file, whereas Pegasus stores the data in an 
            SQL database and Pydpiper saves it a serialized Python object.

@@

    \chapter{Discussion}
    \tristan{You should refer to figure 1 in the text. You could start your discussion by mentioning that
    a summary of your review is available in Figure 1.}
        While mainy neuroimaging workflow engines exist, none of them are well
        suited for the processing of neuroimaging Big Data \tristan{due to? be more specific}. Even more general
        scientific workflows are not equipped for the handling of these datasets.
        Currently existing workflow engines cannot be adapted for Big Data without
        necessitating a major structural changes, as they would need to be converted
        from compute-centric to data-centric. Furthermore, it may not be desirable
        to reuse these frameworks even if adapting them was simple as Big Data 
        frameworks are supported by a much larger community, contributing to 
        more robust workflows.

        Research on the efficiency of Big Data frameworks have been performed 
        and results indicate that Big Data frameworks are effective at 
        improving the performance of scientific workflows. This was even shown
        to be the case when workflows were compute-intensive, as is the case 
        with many neuroimaging frameworks. Performance of Spark and Dask is 
        comparable, however, Dask has been found \weird{to be lose efficiency} during 
        the processing of larger datasets, whereas Spark exhibits reduced 
        performance when significant amounts of shuffling occur. However, both
        of these frameworks need to be adapted to better support the processing
        of scientific data.

        Effective neuroimaging workflows need to meet certain criteria: 
        ease-of-use, performance, portability and reproducibility. In order for
        a workflow language to be easy to use, it is recommended that it is 
        based on simple programming languages commonly used in the field, such 
        as Python or MATLAB (GNU/Octave). Using other programming languages 
        would force researchers to learn a particular language to simply use the
        framework. GUIs are ineffective solutions as they limit the flexibility
        of the pipeline. Moreover, languages such as Python and MATLAB have a 
        diverse set of libraries that can help with processing the data. Big
        Data frameworks such as MapReduce, Spark and Dask all have a Python 
        interface, making them all good candidates for ease-of-use.

@@

    \begin{sidewaysfigure}[!p]
        \centering
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Figures/summary.pdf}
        \caption{Summary table comparing the 17 workflow engines on four axes:
        workflow composition, performance, portability and reproducibility.}
    \end{sidewaysfigure} 
    \addcontentsline{toc}
        {chapter}{Bibliography} 
        \bibliographystyle{ieeetr}
        \bibliography{bibliography}
\end{document}

>>>>

            %\tristan{It could be useful to refer to this special issue on workflows
            %in neuroimaging in intro:
            %https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2844796/}
            %\tristan{This special issue on data sharing is also worth citing:
            %https://www.sciencedirect.com/journal/neuroimage/vol/124/part/PB}
            In contrast, large datasets consist of many images acquired from
            multiple subjects, which are too large to be processed in their
            entirety. Notable examples of these datasets include the 
            Alzheimer's Disease Neuroimaging Initiative 
            (ADNI)~\cite{doi:10.1002/jmri.21049}, 
            OpenfMRI~\cite{POLDRACK2017259}, 
            the Autism Brain Imaging Data Exchange 
            (ABIDE)~\cite{Di-Martino:2013aa}, the Consortium for
            Reliability and Reproducibility (CoRR)~\cite{Zuo:2014aa}, the Human 
            Connectome Project (HCP)~\cite{VANESSEN201362} and the UK 
            Biobank~\cite{Miller:2016aa}, with the later
            two being flagship recent examples of large datasets in 
            neuroimaging.

@@

            OpenfMRI is a public repository originally conceived for the sharing
            of task-based fMRI data. Over time, it has grown to include EEG, MEG,
            resting-state fMRI (R-fMRI) and diffusion fMRI. Data made 
            available through
            OpenfMRI are obtained from both healthy and clinical individuals.
            Raw data must be made available for all datasets published to 
            OpenfMRI, however, preprocessed data may also accompany the raw data
            . At present, OpenfMRI houses data of a total 3372 subjects
            originating from 95 studies.

@@

            The Consortium for Reliability and Reproducibility (CoRR) was developed as an initiative to study 
            and improve the 
            reliability and reproducibility of functional connectomics. The 
            data made available by the Consortium consists of test-retest data 
            obtained from 33 datasets. The repository contains data from 1629 
            subjects, in which anatomical, R-fMRI, dMRI, CBF and ASL scans are 
            available.

@@

            All these initiative stress the importance of data-sharing and
            large-scale studies for the advancement of science. Many researchers
            are limited to the processing of subsets of the data available as 
            they lack compute and storage resources to process the data in its
            entirety. It is also important to note that many of the pipelines 
            developed by these initiatives made use of popular neuroimaging 
            toolboxes, such as FSL~\cite{SMITH2004S208}, FreeSurfer, ANTS, 
            CIVET, rather than
            creating their own. Therefore, there is a great need for Big Data
            frameworks that can leverage existing tools for the efficient 
            processing of large-scale datasets. Widespread availability and 
            accessibility of such frameworks will in turn lead to a greater
            volume of higher-impact studies.

@@

        For a workflow engine to be considered successful, it must be simple to 
        compose workflows using that framework. New researchers should be able 
        to acquire the skills to compose worfklows without
        investing a significant amount of time in understanding it. Reuse of
        existing tools is also common occurrence in neuroinformatics, and 
        workflow engines need to accomodate this by undertaking a modular 
        approach and being easily extensible. With the sharing of data also 
        comes the sharing of workflows. For labs to share their workflows with
        the community at large, these workflows must be easily understood by the
        community. This relates to the reproducibility of studies, as it is 
        more than likely that easily understood workflows are reproducible. 
        %\tristan{Perhaps mention that this also relates to the sharing
        %of reproducible results -- VH: not sure if this is what you meant --
        %yeah, we might want to explicit this further in the paper but
        %good enough for now}}.

@@

            Many researchers have been exposed to Shell scripting languages as 
            several scientific workflows are composed in Linux and OSX-based 
            environments. These environments typically have Make installed by
            default eliminating the need for users to install it manually.
            These features make workflow engine Make desirable for scientific
            computing.
            As Make is exclusive to Linux environments, it is not 
            platform-independent. However, Make has the flexibility of being
            easily extensible and can interface directly with any command-line
            tool. Shell scripting, nevertheless, is generally not as intuitive
            as programming languages like Python and MATLAB.

@@

            Another example of a DSL is the YAML/JSON-based Common Workflow
            Language (CWL). CWL can be seen in workflow engines like Toil and Galaxy.
            CWL is similar to Make, however, it differs from Make in the tasks are 
            isolated. CWL-based workflow engines are platform-independent.

            Programming language-based DSL workflow engines include OpenMOLE, which is  
            derived from Scala, and Nextflow, which is derived from the Apache 
            Groovy programming language. While both are written on top of the 
            Java platform, Nextflow is only compatible with Linux and OSX
            environments. These programming languages are not otherwise commonly
            used in neuroimaging, meaning that users must learn specific 
            languages that would not otherwise be used in their field.

@@

                Performance of workflow engines can be linked to the data structures
                employed by the workflow. Scientific
                workflows are generally file-based, meaning that data in the 
                form of files will be 
                transferred across the network and I/O must be
                performed at each workflow activity. It is possible for some 
                data to remain in memory with scientific workflows, but these 
                are typically basic types such as numbers, strings and lists.
                More complex types, however, can be seen in workflow engines 
                such as PSOM which accept nested structures as long as the
                structures's terminal fields are either strings or cells of 
                strings. Due to workflow engines being file-based, performance
                is limited, particularly with Big Data.

@@

                Dask builds off of Spark by not only providing data 
                structures similar to Spark's RDDs and Dataframes, Dask Bag and 
                DataFrame, but by also providing an abstraction for 
                larger-than-memory matrices, the Dask array. Furthermore, it is
                possible to use Dask clones of common Python APIs (e.g. NumPy~\cite{Oliphant:2015:GN:2886196} and 
                Pandas DataFrame~\cite{mckinney2011pandas}) to process the 
                data. Although Spark does not have a datastructure for large 
                matrices, it has an RDD-based API, known as \textit{linealg}
                for similar processing of large 
                matrices~\cite{BosaghZadeh:2016:MCO:2939672.2939675}.

@@

            Nipype's wrapper, written in Python, can encapsulate command-line interfaces (CLIs), SPM, 
            MATLAB and Python scripts. InputSpec and OutputSpec are two classes 
            that can are used to describe the inputs and outputs of the 
            interface. The former defines the input parameters of 
            a command and the latter defines the outputs that are possibly 
            generated by the command. For CLIs, it is necessary to describe the
            command, such as order of parameters and required and optional parameters. 
            Apart from Input and Output Spec, a Python dictionary containing all
            expected outputs can be included.
            Before executing a CLI, Nipype can start X virtual framebuffer if 
            user interaction through a GUI is required by the tool if specified. 
            For SPM interfaces, the job 
            type and name must be specified. Interfaces to MATLAB require 
            definition of the run function, while Python interfaces require
            the definition of the \textit{\_run\_interface} function.

@@

            OpenMOLE has the ability to encapsulate UDF Scala scripts and CLI. 
            In the case of CLI tasks, it is also possible to containerize or 
            encapsulate with the Comprehensive Archiver for Reproducible Execution (CARE) \cite{Janin:2014:CCA:2618137.2618138} to make it portable. OpenMOLE
            defines several classes to allow for the execution of different 
            types of tools. Like other framworks, it is vital to describe the
            inputs and outputs of the Tasks such that the execution of tasks 
            can be performed.

@@

            LONI enables generation of 
            the XML-based module interface through its GUI. The module interface
            consists of details on module metadata (e.g.
            authors, package, version, name) and citation information, 
            command-line syntax, parameter and file types, dependencies and 
            output and error handling.

@@

            Tool addition in Taverna is primarily performed through the user 
            interface, but can also achieved through the creation of an XML
            descriptor. Taverna differs from other workflow engines in that it
            can 
            execute generic-style services (i.e. WSDL and REST) in addition to
            other types of Web Services, external CLIs, R scripts and
            Java services. To interface with a CLI, the XML file must contain 
            the command to execute, file inputs and outputs (if required), if 
            standard input, output and error streams must be conserved and the 
            location where the command should execute.

            Pegasus is another workflow engine that uses an XML format to 
            define the CLI tools interface. The XML interfaces are typically 
            incorporated directly into the workflow DAX definition. However, a 
            separate multiline text-based 'Transformation Catalogue' file can
            be provided. Information encoded within the interfaces include
            tool identifier (typically namespace::version), the URL or filepath
            to the executable, site identifier of the executable's host, 
            executable type (e.g. installed or staged) and the profile. In
            addition to UDFs and CLIs, Pegasus
            can also execute containerized tools. For this, a container 
            identifier, image URL, site identifier of the image, and container
            profiles must also be defined.

@@

            Big Data frameworks such as MapReduce, Spark and Dask do not have   
            any form of checkpointing functionality outside of a given          
            execution. For instance, it is possible to checkpoint an RDD, but   
            that RDD will only be accessible within the application's context   
            and will not be shared with future executions. As failures do       
            happen and individual neuroimaging tasks may take a non-negligable  
            amount of time to execute, a mechanism to checkpoint workflows      
            will need to be added to any Big Data framework used for             
            neuroinformatics.                                                   
            %\note{dont know how Taverna, Pegasus, Galaxy or Toil achieves this} 
            %\note{openMole says it checks to see if outputs exist. similar to   
            %make?}                                                              
            %\note{what about SPM, FastR??}

@@

            \subsection{NIDM-Results}
                NIDM-results was designed to improve the limited XML-based 
                Clinical and Experimental Data Exchange (XCEDE) neuroimaging
                provenance metadata format~\cite{Maumet:2016aa}. It is a domain-specific extension
                to the W3C PROV model that aims to provide comprehensive and
                machine-readable provenance from raw data to its final stage. %\tristan{give example? -- vhs: like a figure? No, like what can be described which couldn't in BIDS. 
                %Forget about it for the comp exam, keep this note for the paper.}
                However, it is currently limited in the provenance 
                information it can provide, such as details on computational 
                environments. It is also limited by the fact that it is difficult to use and that consensus lacks
                within the community on paradigms. %\tristan{I disagree with the last sentence
                %but this is fine. The main limitation imo is due to the use of RDF and an ontology: it is
                %very powerful but difficult to use: performance sucks, queries are hell to write, 
                %and format is not human-readable.}

@@

            %\tristan{The rest of this section is very difficult to read because
            %it lacks structure. Perhaps you could classify provenance tracking in PROV-based, lineage-based,
            %and other custom formats? -- It is still a bit 'boring' :) No worries for the comp report,
            %but could be discussed and fixed in the paper.}
            At minumum, provenance tracking should include 
            capturing details on the workflow stages as well as the inputs and
            outputs. LONI, Pegasus, Pydpiper and Galaxy all satisfy this 
            requirement, but store the data differently. LONI stores this 
            information in an XML file, whereas Pegasus stores the data in an 
            SQL database and Pydpiper saves it a serialized Python object.

@@

    \chapter{Discussion}

        While mainy neuroimaging workflow engines exist, none of them are well
        suited for the processing of neuroimaging Big Data due to lack of data-centric optimizations. Even more general
        scientific workflows are not equipped for the handling of these datasets.
        Currently existing workflow engines cannot be adapted for Big Data without
        necessitating a major structural changes, as they would need to be converted
        from compute-centric to data-centric. Furthermore, it may not be desirable
        to reuse these frameworks even if adapting them was simple as Big Data 
        frameworks are supported by a much larger community, contributing to 
        more robust workflows.

        Research on the efficiency of Big Data frameworks have been performed 
        and results indicate that Big Data frameworks are effective at 
        improving the performance of scientific workflows. This was even shown
        to be the case when workflows were compute-intensive, as is the case 
        with many neuroimaging frameworks. Performance of Spark and Dask is 
        comparable, however, Dask has been found to become less efficient during 
        the processing of larger datasets, whereas Spark exhibits reduced 
        performance when significant amounts of shuffling occur. However, both
        of these frameworks need to be adapted to better support the processing
        of scientific data.

        Effective neuroimaging workflows need to meet certain criteria: 
        ease-of-use, performance, portability and reproducibility. A summary of
        the workflow engines and how they meet this criteria can be found in Figure~\ref{fig:summary}. In order for
        a workflow language to be easy to use, it is recommended that it is 
        based on simple programming languages commonly used in the field, such 
        as Python or MATLAB (GNU/Octave). Using other programming languages 
        would force researchers to learn a particular language to simply use the
        framework. GUIs are ineffective solutions as they limit the flexibility
        of the pipeline. Moreover, languages such as Python and MATLAB have a 
        diverse set of libraries that can help with processing the data. Big
        Data frameworks such as MapReduce, Spark and Dask all have a Python 
        interface, making them all good candidates for ease-of-use.

@@

    \begin{sidewaysfigure}[!p]
        \centering
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Figures/summary.pdf}
        \caption{Summary table comparing the 17 workflow engines on four axes:
        workflow composition, performance, portability and reproducibility.}
        \label{fig:summary}
    \end{sidewaysfigure} 
    \addcontentsline{toc}
        {chapter}{Bibliography} 
        \bibliographystyle{ieeetr}
        \bibliography{bibliography}
\end{document}
